% Manually add Bibliography to the TOC
\clearpage
\addcontentsline{toc}{chapter}{Bibliography}

% Bibliography starts here
\begin{thebibliography}{99}
    \bibitem{bakshy}
    	{E. Bakshy, J. M. Hofman, W. A. Mason, D. J. Watts. Everyone’s an Influencer: Quantifying Influence on Twitter. In WSDM, pages 65-74, 2011.}
    \bibitem{bass}
    	{F. M. Bass. A new product growth for model consumer
durables. Management Science, 15(5):215–227, 1969.}
    \bibitem{lda}
    	{D. M. Blei, A. Y. Ng, and M. I. Jordan. Latent dirichlet allocation. Journal of Machine Learning Research, 3:993–1022, 2003.}
    \bibitem{pagerank}
    	{S. Brin and L. Page. The anatomy of a large-scale hypertextual web search engine. Computer Network and ISDN Systems, 30(1-7):107–117, 1998.}
    \bibitem{augeas}
    	{A. Farahat, G. Nunberg, and F. Chen. Augeas: authoritativeness grading, estimation, and sorting. In CIKM, pages 194-202, 2002.}
    \bibitem{qalink}
    	{P. Jurczyk and E. Agichtein. Discovering authorities in question answer communities by using link analysis. In CIKM, pages 919-922, 2007.}
    \bibitem{katz}
    	{E. Katz and P. F. Lazarsfeld. Personal influence; the part played by people in the flow of mass communications. Free Press, Glencoe, Ill.” 1955.}
	\bibitem{keller}
    	{E. Keller and J. Berry. The Influentials: One American in Ten Tells the Other Nine How to Vote, Where to Eat, and What to Buy. Free Press, New York, NY, 2003.}
    \bibitem{hits}
    	{J. M. Kleinberg. Authoritative sources in a hyperlinked environment. In SIAM symposium on Discrete algorithms (SODA), pages 668-677, 1998.}
    \bibitem{microblogs}
    	{A. Pal, S. Counts. Finding topical authorities in microblogs. In WSDM, pages 45-54, 2011.}
    \bibitem{qapal}
    	{A. Pal, R. Farzan, J. A. Konstan, R. E. Kraut. Early Detection of Potential Experts in Question Answering Communities. In UMAP, pages 231-242, 2011.}
    \bibitem{rogers}
    	{E. M. Rogers. Diffusion of innovations. Free Press, New York, 4th edition, 1995.}
    \bibitem{twitterrank}
    	{J. Weng, E.-P. Lim, J. Jiang, and Q. He. TwitterRank: finding topic-sensitive influential twitterers. In WSDM, pages 261-270. 2010.}
\end{thebibliography}